Recent Advancements in Neural Computation: \\ \large Differentiable Neural Computers and End-To-End Memory Networks

### 2018-06-16 Paper/Paper.tex
update based on comments

\section{Introduction}
In the last decade, neural networks have considerably revolutionized computation and artificial intelligence. Neural networks have been setting new benchmarks in tasks from a broad range of fields, including computer vision, natural language processing and pattern recognition; many of these tasks previously unsolved, and some of these benchmarks surpassing human-level performance. Until recently, this astounding potential has for the most part been limited to tasks involving sensory processing and representation learning. Memory-centric tasks, i.e. tasks requiring data storage and retrieval, have however proven difficult for neural networks to model. This paper serves as a literature review of two recent approaches towards bypassing this limitation, namely Differentiable Neural Computers\cite{Graves2016} and End-to-End Memory Networks\cite{NIPS2015_5846}. The rest of this section will briefly introduce some important background concepts, before some notation is established in Section \ref{sec:Notation}. The models' details are examined in Sections \ref{DNC} and \ref{E2E}, respectively. Section \ref{Comp} provides a short discussion and a comparative analysis on the two approaches, and Section \ref{Conc} presents some concluding remarks.

A particularly interesting class of neural networks are \textit{Recurrent Neural Networks} (RNNs). Unlike fully-connected networks, which accept a fixed-size input vector and produce a fixed-size output vector over a finite number of computational steps, RNNs instead operate on sequences of vectors. This additional axis of dependencies is captured by a recurrency relation interlinking the network's hidden states through time. More concretely, the hidden representation is no longer conditioned on just the current input, but also on the immediately previous version of itself (Fig.\ref{fig:1}). This elegant addition accounts for a drastic improvement in the representational capacity of the network. Whereas a simple net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs, and is in fact Turing complete\cite{Siegelmann545}. Under this viewpoint, the RNN's hidden representation can be perceived as the program's internal variables, updating as new inputs are received and affecting the computation as it progresses.

@@

Although RNNs have been introduced more than three decades ago, their potential was only recognized recently, as the availability of computational power surged. Their ability to model sequential patterns and their interesting properties have garnered a lot of attention, yet they still suffer from two major drawbacks. The first relates to the statefulness achieved by their intermediate representation; even though it is distributed (hence more expressive than stochastic FSAs or Markov models)\cite[Lecture~10]{Hinton13}, the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage. The second is a more intrinsic one and is not only tied to RNNs but neural networks in general; there is no separation between memory and processing, as each neuron is simultaneously a minimal storage unit and a computational one. Although appealing from a biological perspective, this goes against the von Neumann model and the modern programming paradigm.

A series of advancements has seeked to enhance RNNs with stronger memory management. Starting with the introduction of the \textit{Long Short-Term Memory}\cite{Hochreiter:1997:LSM:1246443.1246450,Gers99learningto}, which permits finite storage over very long computations, research in RNNs has bloomed towards many different directions. One particularly exciting recent advancement is the so-called \textit{attentional interface}\cite{NIPS2014_5542,Bahdanau} (Fig.\ref{fig:2}), which allows a network to selectively shift its focus on particular indices over a set of dimensions of an arbitrary tensor, thus enabling content-based adressing. The implications of this seemingly simple trick are tremendous; when employing fully differentiable attention (soft-attention), a network can learn how to pick out and combine relevant elements out of a (potentially very large) tensor, instead of lossily encoding it. This translates to arbitrary information retrieval; in other words, the same representations can now have different effects on the computation depending on the present context, similar to how a computer program would refer only to the variables dictated by its currently run instruction\cite{NIPS2014_5346}. Since its inception, attention has been a key-concept in many influential publications; the creative liberty it is offering, in terms of new potential operations, has also paved the way for architectures which decouple storage from computation. Such architectures, including but not limited to the two presented in this paper, utilize large external matrices and employ attention to perform read and write operations on them.

@@

		\draw (Ny1)  [dashed] .. controls +(0.8,0.8) and +(-0.8,0.8) ..  (x1);
		\draw (Ny2)  [dashed] .. controls +(3,3) and +(-0.6,0.6) ..  (x2);
		\draw (Ny3)  [dashed] .. controls +(2,-3) and +(0.6,0.4) ..  (xT.west);
	\end{tikzpicture}
	\caption[]
	{\small \textit{}\label{fig:2} General case of an attentional layer. Given some sequence $[\pmb{h}_1,\dots,\pmb{h}_T]$ (e.g. a full sequence of RNN hidden states), we may use an neural function $a$ to obtain a weighting vector $\pmb{a} \in \mathbb{R}^{T}$. Multiplying each sequence element by its corresponding weight and summing up the results, we end up with a context vector $\pmb{c}$. Note that when $a$ accepts an external vector (or vector sequence) as its argument, the result is a context-dynamic selection and linear combination of (parts of) the $[\pmb{h}_1,\dots]$ sequence.}
\end{figure}

@@

\section{Differentiable Neural Computers}
\label{DNC}
\subsection{Description}
Inspired by the von Neumann architecture, DNCs model computation as the interfacing between two units; a RNN controller and an external memory matrix, functioning analogously to the CPU and the RAM, respectively. The memory matrix can be adressed using soft attention mechanisms, allowing selective reading and writing. As both the controller and the interfacing are differentiable, the full architecture is end-to-end differentiable, essentially allowing it to be trained purely with data and minimal human supervision. As the system is already equiped with the necessary tools to simulate traditional computation, i.e. adressing mechanisms, information storage and retrieval, logical flows and arithmetic processing, a DNC in training is learning the instructions of a program rather than the parameters of a function, and a trained DNC should be able to mimic the behavior of a traditionally hand-written program.

\subsection{Architecture}
\paragraph{Overview} 
A differentiable neural computer consists of two main components; a recurrent neural network, called the \textbf{controller network}, and an external \textbf{memory matrix} $M \in \mathbb{R}^{N\times W}$. The matrix contains $N$ memory adresses, each of size $W$, which can be read by the controller through $R$ \textit{read heads}, or written to by one \textit{write head}. At timestep t, the system as a whole receives input in the form of a vector, $\pmb{x}_t \in \mathbb{R}^X$, and produces output in the form of a vector, $\pmb{y}_t \in \mathbb{R}^Y$. The input may be samples from any dataset environment, e.g. some encoding of sensory signals. The output can either represent an approximation for a target vector $\pmb{z}_t \in \mathbb{R}^Y$ (in the supervised learning setting) or encode some action (in the reinforcement learning setting).

@@

	\end{tikzpicture}
	\caption[]
	{\small \textit{}\label{fig:3} High-level view of the DNC. The controller receives continuous input from some external source, which is processed and translated to memory reading/writing and computation instructions. During its operation, the DNC yields a continuous output stream back to the world.}
\end{figure}
\paragraph{Controller}
The aforementioned input is passed to the controller network, alongside the contents of each of the read heads as drawn from the memory at the previous time instance: $\pmb{r}_{t-1}^{i},\ i \in 1, \dots ,R$. The concatenation of the above yields a vector $\pmb{\chi}_t \in \mathbb{R}^{X + RW}: \pmb{\chi}_t = [\pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R ] $. A full sequence of such inputs, $[\pmb{\chi}_1,\dots ,\pmb{\chi}_T]$ is passed through a set of dynamic state equations $\mathcal{N}$, as implemented by the controller, that yield back two intermediate outputs, $\pmb{\upsilon }_T$ and $\pmb{\xi}_T$, such that $\mathcal{N}([\pmb{\chi}_1,\dots,\pmb{\chi}_T]) = (\pmb{\upsilon}_T,\ \pmb{\xi}_T)$. The exact implementation of $\mathcal{N}$ is not essential to the architecture as a whole; $\mathcal{N}$ may be any neural network. Deep long short-term memory networks are the state of the art in sequential modeling, and therefore make for a reasonable choice, since the controller needs to be expressive enough to handle potentially complex data streams.

Out of the vectors $(\pmb{\upsilon}_t,\ \pmb{\xi}_t)$ returned by the controller, the first corresponds to the intermediate user-level output. Before conveying this to the user, the system is allowed one last peak at the memory. This is necessitated by the fact that the read head contents at the final timestep of the computation cannot be used in $\mathcal{N}$, as this would introduce circular dependencies in the architecture's computational graph. The memory conditioning process is therefore done outside the controller, as captured by a simple trainable linear map \begin{equation}
\notag
\pmb{y}_t = \pmb{\upsilon}_t + \pmb{W}_R[\pmb{r}_{t}^1;\dots;\pmb{r}_{t}^R]
\label{eqn:Memory Conditioning}
\end{equation}
The result of the operation is the current instance of the user-level output stream, $\pmb{y}_t$, which represents what the DNC is yielding back to the world while computing.

@@

The remainder of this section is dedicated to examining the role of each of these components.

@@

Each layer applies the memory and output transformations on $pmb{x}$ with each own embedding matrices $A^k, C^k$. The authors, however, explore a few options of weight-sharing in order to reduce the parameter space. One such option is to follow the RNN paradigm, letting all matrices with the same functionality be the same:
\[
\tag{RNN-Tying}
\forall \ (i,j): \pmb{A}^i = \pmb{A}^j, \pmb{C}^i = \pmb{C}^j
\]
This option is of particular interest, as then the network equations would be directly equivalent to those of RNNs, with one subtle but important difference. The intermediate representation $\pmb{p}$, which can be compared with the internal network recurrency, is not a static sample of the memory but rather a softly attended variant, which results in more expressive conditioning of the output on the memory.

@@

\section{Discussion}
\label{Comp}
The previous sections have presented a summary of the design and functionality of two modern approaches towards enhancing recurrent networks with memory. This section will be devoted to some commentary on what the implications of these networks are, how they compare to one another and what their relevance is to computation as a whole.

@@

Differentiable Neural Computers present a concrete, well-thought architecture that can simulate traditional computation via purely differentiable operations. This is one of the very first instantations of a model that falls within the domain of \textit{Probabilistic Programming}\cite{Meijer}, an emerging programming paradigm that proposes treating computer programs as stochastic distributions. Examined end-to-end, Differentiable Neural Computers propose a system capable of learning task-specific memory management and computation. Its practical use cases may be limited for the time being, but the contribution it makes as a whole is clear and rather groundbreaking; that of a single, unified machinery capable of learning programs with vastly different functionalities and input/output data structures; a great leap towards automated program inference. At the same time, the authors pose strong arguments for their design decisions and draw a few interesting parallels between biological intelligence and their system.

Differentiable Neural Computers are the direct successor to Neural Turing Machines\cite{DBLP:journals/corr/GravesWD14}, a related architecture that has the same operative goals but slightly more limited functions. More specifically, Neural Turing Machines lack the ability to perform temporal linking and dynamic memory allocation. This limitation, in turn, disallows them from performing iterative memory retrieval of sequences stored in disparate blocks, and hinders their computational capacities when attempting to reiterate through a previously used memory matrix. Differentiable Neural Computers take specific measures against these problems, as described earlier, and thus excel at both memory allocation and arbitrary sequence retrieval.

@@

End-to-End Networks also draw inspiration from a predecessor paper, namely Memory Networks\cite{DBLP:journals/corr/WestonCB14}, which proposed a very similar architecture. Despite their similarity, End-to-End Networks make a very important contribution over the original paper. Whereas Memory Networks suffer from discontinuities and non-differentiable operations, requiring many levels of human supervision to train, End-to-End Networks resolve these issues by smart application of soft attention. Overall, the idea is easy to replicate and employ, serving as a portable and directly usable alternative to standard choices of sequence processing architectures such as the LSTM, at least for tasks requiring query matching and long-term data dependencies.

\subsection{Computational Relevance}
On another level, neither of the two papers address computation-theoretic problems. They are both very technical in nature, and their orientation is that of an engineering perspective. This does not, by any means, imply a weakness on their part. Neural Networks, and RNNs in particular, are already well-established as powerful machinery for function approximation\cite{Cybenko1989} and are known to be Turing complete\cite{SIEGELMANN1995132}. Improvements over their efficiency, training speed and applicability are nontheless extremely important scientific advancements, and as such both papers do progress the fields of both Artificial Intelligence and Computer Science.

\section{Conclusion}
\label{Conc}
Machine learning has been called, often justifiably, an ad-hoc field, riddled with impulsive design decisions. Enhancing recurrent networks with memory capacities via attentive interfaces is a grounded, logical approach that seeks to shatter this perception. It is a far-reaching idea, deeply rooted in both modern computer science and neurological perspectives of biological intelligence. As such, I believe both of the papers presented are quite significant, as they pave the way for exciting new research and applications of neural computation.

In conclusion, fitting two lengthy technical papers into a brief overview is by no means an easy task. Several details had to be omitted, and some concessions had to be made on the amount of explanatory background provided. Nevertheless, I hope that this paper, as supplemented by the accompanying presentation, has managed to intrigue the interested reader and presented a motivating case towards further researching the topic.

>>>>

\section{Introduction}
In the last decade, neural networks have considerably revolutionized computation and artificial intelligence. Neural networks have been setting new benchmarks in tasks from a broad range of fields, including computer vision, natural language processing and pattern recognition; many of these tasks previously unsolved, and some of these benchmarks surpassing human-level performance. Until recently, this astounding potential has been, for the most part, limited to tasks involving sensory processing and representation learning. Memory-centric tasks, i.e. tasks requiring data storage and retrieval, have however proven difficult for neural networks to model. This paper serves as a literature review of two recent approaches towards bypassing this limitation, namely Differentiable Neural Computers\cite{Graves2016} and End-to-End Memory Networks\cite{NIPS2015_5846}. The rest of this section briefly introduces some important background concepts, before some notation is established in Section \ref{sec:Notation}. The models' details are examined in Sections \ref{DNC} and \ref{E2E}, respectively. Section \ref{Comp} provides a short discussion and a comparative analysis on the two approaches, and Section \ref{Conc} presents some concluding remarks.

A particularly interesting class of neural networks are \textit{Recurrent Neural Networks} (RNNs). Unlike fully-connected networks, which accept a fixed-size input vector and produce a fixed-size output vector over a finite number of computational steps, RNNs instead operate on sequences of vectors. This additional axis of dependencies is captured by a recurrency relation interlinking the network's hidden states through time. More concretely, the hidden representation is no longer conditioned on just the current input, but also on the immediately previous version of itself (Fig.\ref{fig:1}). This elegant addition accounts for a drastic improvement in the representational capacity of the network. Whereas a feedforward net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs, and is in fact Turing complete\cite{Siegelmann545}. Under this viewpoint, the RNN's hidden representation can be perceived as the program's internal variables, updating as new inputs are received and affecting the computation as it progresses.

@@

Although RNNs have been introduced more than three decades ago, their potential was only recognized recently, as the availability of computational power surged. Their ability to model sequential patterns and their interesting properties have garnered a lot of attention, yet they still suffer from two major drawbacks. The first relates to the statefulness achieved by their intermediate representation; even though it is distributed (hence more expressive than stochastic FSAs or Markov models)\cite[Lecture~10]{Hinton13}, the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage. The second drawback is a more intrinsic one and is not only tied to RNNs but neural networks in general; there is no separation between memory and processing, as each neuron is simultaneously a minimal storage unit and a computational one. Although appealing from a biological perspective, this goes against the von Neumann model and the established programming paradigm.

A series of advancements has seeked to enhance RNNs with stronger memory management. Starting with the introduction of the \textit{Long Short-Term Memory}\cite{Hochreiter:1997:LSM:1246443.1246450,Gers99learningto}, which permits finite storage over very long computations, research in RNNs has bloomed towards many different directions. One particularly exciting recent advancement is the so-called \textit{attentional interface}\cite{NIPS2014_5542,Bahdanau} (Fig.\ref{fig:2}), which allows a network to selectively shift its focus on particular indices over a set of dimensions of an arbitrary tensor, thus enabling content-based adressing. The implications of this seemingly simple trick are tremendous; when employing fully differentiable attention (soft-attention), a network can learn how to pick out and combine relevant elements out of a (potentially very large) tensor, instead of lossily encoding it. This translates to arbitrary information retrieval; in other words, the same representations can now have different effects on the computation depending on the present context, similar to how a computer program would refer only to the variables dictated by its currently run instruction\cite{NIPS2014_5346}. Since its inception, attention has been a key-concept in many influential publications; the creative liberty it is offering, in terms of new potential operations, has also paved the way for architectures which decouple storage from computation. Such architectures, including (but not limited to) the two presented in this paper, utilize large external matrices and employ attention to perform read and write operations on them.

@@

		\draw (Ny1)  [dashed] .. controls +(0.8,0.8) and +(-0.8,0.8) ..  (x1);
		\draw (Ny2)  [dashed] .. controls +(3,3) and +(-0.6,0.6) ..  (x2);
		\draw (Ny3)  [dashed] .. controls +(2,-3) and +(0.6,0.4) ..  (xT.west);
	\end{tikzpicture}
	\caption[]
	{\small \textit{\label{fig:2} General case of an attentional layer. Given some sequence $[\pmb{h}_1,\dots,\pmb{h}_T]$ (e.g. a full sequence of RNN hidden states), we may use an neural function $a$ to obtain a weighting vector $\pmb{a} \in \mathbb{R}^{T}$. Multiplying each sequence element by its corresponding weight and summing up the results, we end up with a context vector $\pmb{c}$. Note that when $a$ accepts an external vector (or vector sequence) as its argument, the result is a context-dynamic selection and linear combination of (parts of) the $[\pmb{h}_1,\dots]$ sequence.}}
\end{figure}

@@

\section{Differentiable Neural Computers}
\label{DNC}
\subsection{Description}
Inspired by the von Neumann architecture, Differentiable Neural Computers (or DNCs in short) model computation as the interfacing between two units; a RNN controller and an external memory matrix, functioning analogously to the CPU and the RAM, respectively. The memory matrix can be adressed using soft attention mechanisms, allowing selective reading and writing. As both the controller and the interfacing are differentiable, the full architecture is end-to-end differentiable, essentially allowing it to be trained purely with data and minimal human supervision. As the system is already equiped with the necessary tools to simulate traditional computation, i.e. adressing mechanisms, information storage and retrieval, logical flows and arithmetic processing, a DNC in training is learning the instructions of a program rather than the parameters of a function. A trained DNC should then be able to mimic the behavior of a traditionally hand-written program.

\subsection{Architecture}
\paragraph{Overview} 
A differentiable neural computer consists of two main components; a neural network, called the \textbf{controller network}, and an external \textbf{memory matrix} $M \in \mathbb{R}^{N\times W}$. The matrix contains $N$ memory adresses, each of size $W$, which can be read by the controller through $R$ \textit{read heads}, or written to by one \textit{write head}. At timestep t, the system as a whole receives input in the form of a vector, $\pmb{x}_t \in \mathbb{R}^X$, and produces output in the form of a vector, $\pmb{y}_t \in \mathbb{R}^Y$. The input may be samples from any dataset environment, e.g. some encoding of sensory signals. The output can either represent an approximation for a target vector $\pmb{z}_t \in \mathbb{R}^Y$ (in the supervised learning setting) or encode some action (in the reinforcement learning setting).

@@

	\end{tikzpicture}
	\caption[]
	{\small \textit{\label{fig:3} High-level view of the DNC. The controller receives continuous input from some external source, which is processed and translated to memory reading/writing and computation instructions. During its operation, the DNC yields a continuous output stream back to the world.}}
\end{figure}
\paragraph{Controller}
The aforementioned input is passed to the controller network, alongside the contents of each of the read heads as drawn from the memory at the previous time instance: $\pmb{r}_{t-1}^{i},\ i \in 1, \dots ,R$. The concatenation of the above yields a vector $\pmb{\chi}_t \in \mathbb{R}^{X + RW}: \pmb{\chi}_t = [\pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R ] $. A full sequence of such inputs, $[\pmb{\chi}_1,\dots ,\pmb{\chi}_T]$ is passed through a set of dynamic state equations $\mathcal{N}$, as implemented by the controller, that yield back two intermediate outputs, $\pmb{\upsilon }_T$ and $\pmb{\xi}_T$, such that $\mathcal{N}([\pmb{\chi}_1,\dots,\pmb{\chi}_T]) = (\pmb{\upsilon}_T,\ \pmb{\xi}_T)$. The exact implementation of $\mathcal{N}$ is not essential to the architecture as a whole; $\mathcal{N}$ may be any neural network. Deep long short-term memory networks are the state of the art in sequential modeling, and therefore make for a reasonable choice, since the controller needs to be expressive enough to handle potentially complex data streams.

Out of the vectors $(\pmb{\upsilon}_t,\ \pmb{\xi}_t)$ returned by the controller, the first corresponds to the intermediate user-level output. Before conveying $\pmb{\upsilon}_t$ to the user, the system is allowed one last peak at the memory. This is necessitated by the fact that the read head contents at the final timestep of the computation cannot be used in $\mathcal{N}$, as this would introduce circular dependencies in the architecture's computational graph. The memory conditioning process is therefore done outside the controller, as captured by a simple trainable linear map \begin{equation}
\notag
\pmb{y}_t = \pmb{\upsilon}_t + \pmb{W}_R[\pmb{r}_{t}^1;\dots;\pmb{r}_{t}^R]
\label{eqn:Memory Conditioning}
\end{equation}
The result of the operation is the current instance of the user-level output stream, $\pmb{y}_t$, which represents what the DNC is yielding back to the world while computing.

@@

The remainder of this section is dedicated to examining the role of each of these components, in the context of the network's broader functionalities.

@@

Each layer applies the memory and output transformations on $\pmb{x}$ with each own embedding matrices $A^k, C^k$. The authors, however, explore a few options of weight-sharing in order to reduce the parameter space. One such option is to follow the RNN paradigm, letting all matrices with the same functionality be the same:
\[
\tag{RNN-Tying}
\forall \ (i,j): \pmb{A}^i = \pmb{A}^j, \pmb{C}^i = \pmb{C}^j
\]
This option is of particular interest, as then the network equations would be directly equivalent to those of RNNs, with one subtle but important difference. The intermediate representation $\pmb{p}$, which can be compared with the internal network recurrency, is not a static sample of the memory but rather a softly attended variant, which results in more expressive conditioning of the output on the memory.

@@

\section{Discussion}
\label{Comp}
The previous sections have presented a summary of the design and functionality of two modern approaches towards enhancing recurrent networks with memory. This section is devoted to some commentary on what the implications of these networks are, how they compare to one another and what their relevance is to computation in general.

@@

Differentiable Neural Computers present a concrete, well-thought architecture that can simulate traditional computation via purely differentiable operations. This is one of the very first instantations of a model that falls within the domain of \textit{Probabilistic Programming}\cite{Meijer}, an emerging programming paradigm that proposes treating computer programs as stochastic distributions. Examined end-to-end, DNCs propose a system capable of learning task-specific memory management and computation. Its practical use cases may be limited for the time being, but the contribution it makes as a whole is clear and rather groundbreaking; that of a single, unified machinery capable of learning programs with vastly different functionalities and input/output data structures; a great leap towards automated program inference. At the same time, the authors pose strong arguments for their design decisions and draw a few interesting parallels between biological intelligence and their system

DNCs are the direct successor to Neural Turing Machines\cite{DBLP:journals/corr/GravesWD14}, a related architecture that has the same operative goals but slightly more limited functions. More specifically, Neural Turing Machines lack the ability to perform temporal linking and dynamic memory allocation. This limitation, in turn, disallows them from performing iterative memory retrieval of sequences stored in disparate blocks, and hinders their computational capacities when attempting to reiterate through a previously used memory matrix. DNCs take specific measures against these problems, as described earlier, and thus excel at both memory allocation and arbitrary sequence retrieval.

@@

End-to-End Networks also draw inspiration from a predecessor paper, namely Memory Net-
works\cite{DBLP:journals/corr/WestonCB14}, which proposed a very similar architecture. Despite their similarity, End-to-End Networks make a very important contribution over the original paper. Whereas Memory Networks suffer from discontinuities and non-differentiable operations, requiring many levels of human supervision to train, End-to-End Networks resolve these issues by smart application of soft attention. Overall, the idea is easy to replicate and employ, serving as a portable and directly usable alternative to standard choices of sequence processing architectures such as the LSTM, at least for tasks requiring query matching and long-term data dependencies.

On another level, neither of the two papers address computation-theoretic problems. This does not, by any means, imply a weakness on their part. Neural Networks, and RNNs in particular, are already well-established as powerful machinery for function approximation\cite{Cybenko1989} and are known to be Turing complete\cite{SIEGELMANN1995132}. Improvements over their efficiency, training speed and applicability are nontheless extremely important engineering advancements, and as such both papers do progress the fields of both Artificial Intelligence and Computer Science, albeit from an applied standpoint.

\section{Conclusion}
\label{Conc}
Machine learning has been called, often justifiably, an ad-hoc field, riddled with impulsive design decisions. Enhancing recurrent networks with memory capacities via attentive interfaces is a grounded, logical approach that seeks to shatter this perception. It is a far-reaching idea, deeply rooted in both modern computer science and neurological perspectives of biological intelligence. Consequently, I believe both of the papers presented are of great significance, as they pave the way for exciting new research and applications of neural computation.

To conclude, fitting two lengthy technical papers into a brief overview is by no means an easy task. Several details had to be omitted, and some concessions had to be made on the amount of explanatory background provided. Nevertheless, I hope that this paper, as supplemented by the accompanying presentation, has managed to intrigue the interested reader and presented a motivating case towards further researching the subject.
